\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-26 pldi/draft.tex
Checkpoint

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{\sys's speedup for 2--6$\times$-parallelism.} 
      Different configurations per benchmark:
      (i) Par+Split: \ttt{eager} and general \ttt{split} enabled,
      (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (iii) Parallel: \ttt{eager} enabled (no \ttt{split}),
      (v) Blocking Eager, only blocking \ttt{eager} enabled (no \ttt{split}),
      (iv) No Eager: both \ttt{eager} and \ttt{split} disabled,
      (vi) Opt. Parallel, an optimized version of \ttt{bigrams}~\cf{ours}.
      Only relevant configurations are shown---\eg \ttt{grep} and \ttt{sort} do not benefit from \ttt{split}; \ttt{spell} and \ttt{bi-grams} do not see benefits without \ttt{split}.
      % TODO: WHY?
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

Existing techniques for exploiting parallelism are not directly comparable to \sys, either because they requiresignificantly more \emph{user} effort (see \sx{intro} for distinction between users and developers); or are too specialized, targeting narrow domains or custom programming abstractions.
%% Techniques for re-writing programs to exploit parallelism fall under a wide spectrum that ranges from fully manual (but, ideally, optimal or more general) to fully automated (but potentially sub-optimal or specialized).
%% \kk{It is not very clear what the following sentence tries to achieve.}
%% Following the distinction between \emph{users} and \emph{developers} established earlier~\sx{intro}, we note correctness trade-offs associated with approaches that require user input for the discussion below:
%%    users---often neither experts in parallelism nor educated on the internals of the code they depend on---can easily break the correctness of sequential programs, especially when these depend on existing code (such as is the case with shell commands).

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{\detokenize{./figs/tiling_throughput_scaleup.pdf}}
    \caption{
      \textbf{\sys's speedup for 2--6$\times$-parallelism.} 
      Different configurations per benchmark:
      (i) Par+Split: \ttt{eager} and general \ttt{split} enabled,
      (ii) Par+B.Split: \ttt{eager} and input-aware \ttt{split} enabled,
      (iii) Parallel: \ttt{eager} and \ttt{split} disabled,
      (iv) No Eager: only \ttt{split} enabled,
      (v) Blocking Eager, only \todo{naive blocking} \ttt{eager} enabled (no \ttt{split},
      (vi) Opt. Parallel, an optimized version of \ttt{bigrams}~\cf{ours}.
      Only relevant configurations are shown---\eg \ttt{grep} and \ttt{sort} do not benefit from \ttt{split}; \ttt{spell} and \ttt{bi-grams} do not see benefits without \ttt{split}.
      % TODO: WHY?
    }
    \vspace{-15pt}
    \label{fig:microbenchmarks}
\end{figure*}

@@

Many prior techniques for exploiting parallelism are not directly comparable with \sys, either because they require significantly more \emph{user} effort (see \S\ref{intro} for distinction between users and developers) 
  or because they are too specialized, targeting narrow domains or custom programming abstractions.
%% Techniques for re-writing programs to exploit parallelism fall under a wide spectrum that ranges from fully manual (but, ideally, optimal or more general) to fully automated (but potentially sub-optimal or specialized).
%% \kk{It is not very clear what the following sentence tries to achieve.}
%% Following the distinction between \emph{users} and \emph{developers} established earlier~\sx{intro}, we note correctness trade-offs associated with approaches that require user input for the discussion below:
%%    users---often neither experts in parallelism nor educated on the internals of the code they depend on---can easily break the correctness of sequential programs, especially when these depend on existing code (such as is the case with shell commands).
